\sysfull

### 2018-08-03 paper/asplos19/background.tex
partial commit

\textbf{Hardware Assumptions.} \sys is designed for the demands of existing and
future energy-harvesting platforms based around general purpose, commodity
computing components~\cite{wisp,msp430datasheet}. We assume a device with a
memory system that has fast, byte-addressable volatile and non-volatile memory;
in particular, our target platform, WISP~\cite{wisp}, is equipped with a
mixture of SRAM and FRAM. Our implementation leverages hardware support for
fast, bulk-copying between memories via DMA~\cite{msp430datasheet}. \sys do not
require architectural additions to commodity processors as
in~\cite{su_date_2017,hicks_isca_2017,quickrecall,nvp}.

@@

Task-based execution models~\cite{dino,chain,alpaca} ask the programmer to
decompose their program into \textbf{tasks}, which is a region of code that can contain
arbitrary computation, sensing, and communication.  Task-based models keep
progress at the granularity of tasks by repeatedly trying to re-execute each
task on power failure until it successfully finishes, only then moving on to
the next task.  Since these models do not rely on taking an expensive
checkpoint, it is usually faster than the checkpoint-based
solution~\cite{chain, alpaca}.  \sys also follows the paradigm of the
task-based programming model, where the programmer explicitly expresses the
application as a sequence of tasks and the transition between them.
%Task-based runtime systems ensure that repeated task executions are idempotent. 
%The key to idempotence is ensuring that non-volatile updates made by an interrupted task are never visible to a future task execution.  
%A programmer describes task control-flow as a {\em task graph}. Task flow happens at programmer demarcated transition points that may be conditional on program values. 
%Task-based programming abstractions guarantee that tasks execute {\em atomically}, regardless of power failures.

>>>>

\textbf{Hardware Assumptions.} \sys is designed for the demands of existing and
future energy-harvesting platforms based around general purpose, commodity
computing components~\cite{wisp,msp430datasheet}. We assume a device with a
memory system that has fast, byte-addressable volatile and non-volatile memory;
in particular, our target platform, WISP~\cite{wisp}, is equipped with a
mixture of SRAM and FRAM. Our implementation leverages hardware support for
fast, bulk-copying between memories via DMA~\cite{msp430datasheet}. \sys does not
require architectural additions to commodity processors as
in~\cite{su_date_2017,hicks_isca_2017,quickrecall,nvp}.

@@

Task-based execution models~\cite{dino,chain,alpaca} ask the programmer to
decompose their program into \textbf{tasks}, which is a region of code that can contain
arbitrary computation, sensing, and communication.  Task-based models keep
progress at the granularity of tasks by repeatedly trying to re-execute each
task on power failure until it successfully finishes, only then moving on to
the next task.  Since these models do not rely on taking an expensive
checkpoint, it is usually faster than the checkpoint-based
solution~\cite{chain, alpaca}.  \sys also follows the paradigm of the
task-based programming model, where the programmer explicitly expresses the
application as a sequence of tasks and the transitions between them.
%Task-based runtime systems ensure that repeated task executions are idempotent. 
%The key to idempotence is ensuring that non-volatile updates made by an interrupted task are never visible to a future task execution.  
%A programmer describes task control-flow as a {\em task graph}. Task flow happens at programmer demarcated transition points that may be conditional on program values. 
%Task-based programming abstractions guarantee that tasks execute {\em atomically}, regardless of power failures.

### 2018-08-03 paper/asplos19/systemdescription.tex
partial commit

\textbf{Programming and Execution Model.}  To use \sys, a programmer first writes plain, imperative C code. The programmer then must decompose the program into tasks. To manually decompose a program into tasks, the programmer designates a set of functions as tasks, sequences control-flow between these tasks, and annotates memory accesses that manipulate data shared by multiple tasks. In other words, it requires reasoning similar to prior task-based systems~\cite{chain,alpaca}.

A programmer may also opt to use compiler support to automatically decompose a program into tasks, leveraging recent work~\cite{cleancut_2018,baghsorkhi_cgo_2018}. Without loss of generality, we assume throughout this work that the programmer manually decomposed the program into tasks; \sys's behavior with automatically decomposed code would be identical.

The programmer compiles their task-based code, and links to \sys runtime,
producing a \sys-enabled binary. The runtime implements \sys's task-based
programming and execution model. The runtime system also includes \sys's novel
{\em virtual memory manager} and its {\em adaptive task scheduler}, both
of which are essential to \sys's adaptive task-based execution.

>>>>

\textbf{Programming and Execution Model.}  To use \sys, a programmer must convert a plain C code into tasks by  designates a top-level set of functions as tasks, sequences the control-flow between these tasks, and annotates memory accesses that manipulate global data.
% In other words, it requires reasoning similar to prior task-based systems~\cite{chain,alpaca}.

% A programmer may also opt to use compiler support to automatically decompose a program into tasks, leveraging recent work~\cite{cleancut_2018,baghsorkhi_cgo_2018}. Without loss of generality, we assume throughout this work that the programmer manually decomposed the program into tasks; \sys's behavior with automatically decomposed code would be identical.

The programmer compiles their task-based code, and links to \sys runtime,
producing a \sys-enabled binary. The runtime library relies on \sys's novel
{\em virtual memory manager} and its {\em adaptive task scheduler} to execute the binary 
efficiently.
